Efficient Handling of String-Number Conversion

### 2019-11-21 evaluation.tex

We compare {\tool} with other state-of-the-art string solvers, namely CVC4~(relese-1.7)~\cite{cvc4Tool}, Z3~(\texttt{dde8da853})~\cite{z3}, \textsf{Z3-str3}~(\texttt{109dfc5e8})~\cite{zheng2013z3}, \textsf{Trau+}~\cite{parosh2019chain}, , and Ostrich~\cite{chen2019decision}. We do not compare with Sloth \cite{sloth} since it does not support length constraints, which occurs in most of our benchmarks. We also do not compare with ABC~\cite{aydin2018parameterized} (a model counter for string constraints), which over-approximates cases that cannot be modeled by \emph{aligned multi-track automata}~\cite{yu2016optimal} and hence cannot solve our benchmark examples precisely.

We perform two sets of experiments. In the first experiment, we compare with other tools on benchmarks over basic string constraints. We use the following benchmark examples in this experiments:
\begin{itemize}
	\item PyEx~\cite{pyex} is from running the symbolic executor PyEx over some Python packages.
	\item APLAS~\cite{aplas} includes 600 hand-drafted tests consisting of only equality and integer length constraints.
	\item LeetCode is from running PyEx over some sample code collected from the LeetCode~\cite{LeetCode} website.
	\item StringFuzz~\cite{StringFuzz}  is generated from the fuzz testing tool of the same name.
	\item $\text{cvc4}_{\text{pred}}$ and $\text{cvc4}_{\text{term}}$ are obtained from the CVC4 group~\cite{termEQ}. These benchmarks contain a small amount of string-number conversion constraints (< $5\%$).
\end{itemize}

>>>>

We compare {\tool} with other state-of-the-art string solvers, namely CVC4~(relese-1.7)~\cite{cvc4Tool}, Z3~(\texttt{dde8da853})~\cite{z3}, \textsf{Z3-str3}~(\texttt{109dfc5e8})~\cite{zheng2013z3}, \textsf{Trau+}~\cite{abdulla2019chain}, , and Ostrich~\cite{chen2019decision}. We do not compare with Sloth \cite{sloth} since it does not support length constraints, which occurs in most of our benchmarks. We also do not compare with ABC~\cite{aydin2018parameterized} (a model counter for string constraints), which over-approximates cases that cannot be modeled by \emph{aligned multi-track automata}~\cite{yu2016optimal} and hence cannot solve our benchmark examples precisely.

We perform two sets of experiments. In the first experiment, we compare with other tools on benchmarks over basic string constraints. We use the following benchmark examples in this experiments:
\begin{itemize}
	\item PyEx~\cite{pyex} is from running the symbolic executor PyEx over some Python packages.
	\item APLAS~\cite{aplas} includes 600 hand-drafted tests consisting of only equality and integer length constraints.
	\item LeetCode is from running PyEx over some sample code collected from the LeetCode~\cite{LeetCode} website.
	\item StringFuzz~\cite{blotsky2018stringfuzz}  is generated from the fuzz testing tool of the same name.
	\item $\text{cvc4}_{\text{pred}}$ and $\text{cvc4}_{\text{term}}$ are obtained from the CVC4 group~\cite{termEQ}. These benchmarks contain a small amount of string-number conversion constraints (< $5\%$).
\end{itemize}
